BioTime

### 2021-03-11 data-raw/02_biotime_ids.Rmd

### Or, from the grid processing script
```{r}
#file created by 01_biotime_grid.R
pins::board_register_github(name = "github", repo = "karinorman/biodivTS_data", branch = "master")
bt_grid_col <- pins::pin_get("bt-grid-collate", board = "github")

data <- bt_grid_col %>%
  rename_with(tolower) %>%
  mutate(species = str_replace(species, "_", " "))

rm(bt_grid_col)
```

>>>>

### Or, from the grid processing script
```{r}
#file created by 01_biotime_grid.R
bt_grid <- pins::pin_get("bt-grid", board = "github_data")

data <- bt_grid %>%
  rename_with(tolower) %>%
  mutate(species = str_replace(species, "_", " "))

rm(bt_grid)
```
